### 2021-12-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@00313593cd843082ea8043d1bff842745e049e2d 🚀

The dataset used for numerical experiments is composed of 20000 such
\((\xi, \nu)\) pairs, on which four learners are trained: a decision
tree regressor, a boosted regression tree, a ridge regressor, and a
random forest regressor. All models were taken from the \texttt{MLJ.jl}
package (Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7
(Bezanson et al., 2017). In order to pick the best adjacency matrix for
a given learner, we performed a thresholding approach using 500 steps on
predictions from the testing set, and picking the threshold that
maximized Youden's informedness, which is usually the optimized target
for imbalanced classification. During the thresholding step, we measured
the area under the receiving-operator characteristic (ROC-AUC) and
precision-recall (PR-AUC) curves, as measures of overall performance
over the range of returned values. We report the ROC-AUC and PR-AUC, as
well as a suite of other measures as introduced in the next section, for
the best threshold. The ensemble model was generated by summing the
predictions of all component models on the testing set (ranged in
\([0,1]\)), then put through the same thresholding process. The complete
code to run the simulations is given as an appendix.

@@

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. This research was enabled in part by support provided by Calcul
Québec (www.calculquebec.ca) and Compute Canada (www.computecanada.ca).

>>>>

The dataset used for numerical experiments is composed of 64000 such
\((\xi, \nu)\) pairs, on which four learners are trained: a decision
tree regressor, a boosted regression tree, a ridge regressor, and a
random forest regressor. All models were taken from the \texttt{MLJ.jl}
package (Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7
(Bezanson et al., 2017). In order to pick the best adjacency matrix for
a given learner, we performed a thresholding approach using 500 steps on
predictions from the testing set, and picking the threshold that
maximized Youden's informedness, which is usually the optimized target
for imbalanced classification. During the thresholding step, we measured
the area under the receiving-operator characteristic (ROC-AUC) and
precision-recall (PR-AUC) curves, as measures of overall performance
over the range of returned values. We report the ROC-AUC and PR-AUC, as
well as a suite of other measures as introduced in the next section, for
the best threshold. The ensemble model was generated by summing the
predictions of all component models on the testing set (ranged in
\([0,1]\)), then put through the same thresholding process. The complete
code to run the simulations is given as an appendix; running the final
simulation required 4.8 core days (approx. 117 hours).

@@

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. This research was enabled in part by support provided by Calcul
Québec (www.calculquebec.ca) and Compute Canada (www.computecanada.ca)
through the Narval general purpose cluster. TP is supported by a NSERC
Discovery Grant and Discovery Acceleration Supplement, and by a grant
from the Institut de Valorisation des Données (IVADO).
